Breeding bird indicators

### 2023-10-19 Nature_Index_product.Rmd
#151

```{r, echo=F}
metaData <- data.frame(Ecosystem,
                       "Økologisk egenskap" = Egenskap,
                       "ECT class" = ECT,
                       check.names = F)
knitr::kable(metaData)
```

>>>>

```{r, echo=F}
metaData <- data.frame(Ecosystem,
                       "Økologisk egenskap" = Egenskap,
                       "ECT class" = ECT,
                       check.names = F)
flextable(metaData) %>%
  bg(bg = "lightblue", part="header") %>%
  theme_vanilla() %>%
  set_table_properties(layout = "autofit")
```
